Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-07 src/article.tex
Revise discussion section

Scaffolding requires joining assembled contigs and insert additional sequence
data using a combination of computational and laboratory methods. The process
of manually editing a scaffold is inherently hard to reproduce and introduces
the possibility of human error. The aims of this Scaffolder software are
therefore twofold. The first is providing software that is easy to install and
simplifies the task of genome finishing. The second aim is to facilitate
reproducibility when joining large nucleotide sequences together to create
a genome sequence. \pb

Scaffolder was designed to be as simple to use and, assuming the Ruby and
RubyGems software are present, Scaffolder can be installed in a single command
line step. This should negate any possible barriers to entry which require
manual compilation of source code. Scaffolder also uses a minimal and compact
syntax to describe the genome scaffold. This syntax is simple to construct and
edit whilst being succinct and readable. The goal of this syntax is to make
genome scaffolds easy to make in a common text editor. The use of word
processors for this task is however discouraged. \pb

>>>>

Scaffolding requires joining assembled contigs and insert additional sequence
data using a combination of computational and laboratory methods. The process
of manually editing a scaffold is inherently hard to reproduce and introduces
the possibility of irreporducible techniques and/or human error. The aims of
the Scaffolder software are twofold: 1) to provide software that is easy to
install and simplifies the task of genome finishing; and 2) to facilitate
reproducibility when joining large nucleotide sequences together to create
a genome sequence. \pb

Scaffolder was designed to be as simple to use and, assuming the Ruby and
RubyGems software are present, Scaffolder can be installed in a single command
line step. This should negate any possible barriers to entry which require
manual compilation of source code. Scaffolder also uses a minimal and compact
syntax to describe the genome scaffold. This syntax is simple to construct and
edit whilst being succinct and readable. The goal of this syntax is to make
genome scaffolds easy to make in a common text editor; however the use of word
processors for this task is discouraged. \pb
